Equalizer 2.0 --\\Convergence of a Parallel Rendering Framework

### 2018-08-01 paperIEEE.tex
Reviewer 3, comment 1
git-svn-id: https://dev.ifi.uzh.ch/vmml/svn/Equalizer16@141 db7c848b-7755-4df2-b763-8796797afa52

Time-multiplexing (\fig{fig:dplex}), also called AFR or DPlex, was first
implemented in \cite{BRE:05} for shared memory machines. It is however a better
fit for distributed memory systems, since the separate memory space makes
concurrent rendering of different frames easier to implement. While it increases
the framerate linearly, it does not decrease the latency between user input and
the corresponding output. Consequently, this decomposition mode is mostly useful
for non-interactive movie generation. It is transparent to \textsf{Equalizer}
applications, but does require the configuration latency to be equal or greater
than the number of source channels. Furthermore, to work in multi-threaded,
multi-GPU configurations, the application needs to support running the rendering
threads asynchronously (\sref{sec:threading}). The output frame rate of the
destination channel may be smoothened using a {\em frame rate equalizer}
(\sref{sec:framerateEq}).

@@

@@

@@

% Furthermore, subpixel compounds interact with idle image refinements, e.g., they
% can accelerate idle anti-aliasing of a scene when the camera and scene are not
% changed.

>>>>

Time-multiplexing (\fig{fig:dplex}), also called AFR or DPlex, was first
implemented in \cite{BRE:05} for shared memory machines. It is however a better
fit for distributed memory systems, since the separate memory space makes
concurrent rendering of different frames easier to implement. While it
increases the framerate linearly, it does not decrease the latency between user
input and the corresponding output. Consequently, this decomposition mode is
mostly useful for non-interactive rendering, e.g., for movie generation. It is
transparent to \textsf{Equalizer} applications, but does require the
configuration latency to be equal or greater than the number of source
channels. Furthermore, to work in multi-threaded, multi-GPU configurations, the
application needs to support running the rendering threads asynchronously
(\sref{sec:threading}). The output frame rate of the destination channel may be
smoothened using a {\em frame rate equalizer} (\sref{sec:framerateEq}).

DPlex is configured by restricting the source compounds to a \textit{phase}
(offset) of a certain \textit{period} (number of skipped frames) of the
destination channel's rendering. All output frames of the source channels may
use the same name, as each output frame only is available at a distinct
rendered frame for input. The period/phase decomposition may also be used for
other means, e.g., to have one channel render at half the frame rate on an
underpowered control workstation for a tiled display wall.

@@

Tile and chunk compounds are configured through output and input queues, which
behave similarly to compositing frames. A single output queue configures the
tile or chunk size and generates the work packages on the destination compound.
Each source has an input queue of the same name, which consumes items from the
output queue. Each work item generates a separate draw and readback task, and
one input assemble image on the destination channel.

@@

Pixel compounds are configured similarly to sort-first compounds, except that
instead of decomposing the \textit{viewport}, they decompose a \textit{pixel}
kernel. The kernel is a 2D structure describing the shape and sampled pixel
within the shape in the format \textit{[x y width height]}, that is, a source
compound selects the pixel \textit{x, y} within a decomposition of size
\textit{width, height}.

@@

Subpixel compounds are configured similarly to pixel compounds, but instead of
a \textit{pixel} kernel they decompose a \textit{subpixel} kernel in the format
\textit{[index, size]}, describing which subpixel of \textit{size} samples a
source produces. By default, the output frames are averaged on the destination
channel.
